Practice Problems

### 2023-10-04 Stats Rethinking/Ch9/Practice Problems.qmd
Finished some hards

# 9H1

@@

@@

@@

>>>>

# 9H1\*

@@

Compare this samples for the parameters `a` and `b`. Can you explain the different trace plots? If you are unfamiliar with Cauchy distribution, you should look it up. The key feature to attend to is that it has no expected value/ Can you connect this fact to the trace plot?

@@

```{r}
traceplot(mp)
```

I'm not going to lie, I have no idea what this is doing or trying to accomplish. It also does look like for `b` that there is an expected value that it settles to, at least for this run.

@@

Modify the Metropolis algorithm code from the chapter to handle the case that the island populations have a different distribution than the island labels. This means that the island's number will not be the same as its population.
